\subsection*{D3}
    \hfill \break
    The current global situation was a massive challenge to the group. Not only did it effect how the group met and communicated in which was the first group project started during the pandemic for all of us, but this period has also been a significant struggle and has effected academic performance for some of the members in the group.\\
    
    The fact that we were physically apart meant communication was limited to calls, texts and emails. Because these forms of communication are inherently more limited than face-to-face conversing it was important that we we communicate, we clearly define the goals of it. Things like the issue tracker in GitHub was key to ensuring we were all on the same page when it came to progress and outstanding tasks. In hindsight weekly voice or video meetings should've been implemented as although the group had constant contact through social media it was difficult to stay motivated for some members in the group especially in the aforementioned global situation.\\
    
    The coursework assignment was structured more linearly than expected which didn't inherently enable a simultaneous workflow. This meant that even though we started earlier than most groups we were still pushed for time as we found that tasks had to be completed in a set order and the way tasks were distributed in the beginning meant that group members were sometimes left waiting for someone to finish a task. This could've been helped by encouraging more people to engage with every task rather than splitting tasks up as you would in a traditional workload.\\
    
    Finally, towards the submission dealing David started showing symptoms of COVID-19. Thankfully he tested negative in the following days however this was added stress to an already stressful situation and coursework due to the amount of work needed to complete it. However, Ben and Cerys managed to rise up to the challenge and get a version of this coursework submitted in time in case David's exceptional circumstances form was rejected.
